---
title: "R language"
author: "H24066147"
output: 
  html_document:  
    toc : true
    toc_depth : 2
    toc_float :
      collapsed : false
      smooth_scroll : false
---
#CH1  **basic**  

   + basic math  
   
    
```5+49```

```3*10```

```2-5```

```1/0```
##inf 

```0/0```
##NaN

```3^4```
##81

```31%%7```
##3

```31%/%7```
##4

```Inf - Inf```
##NaN

   + basic function

```ls()```
##see the variable

```q()```
##leave the programming


```mean()```
##cal mean

```var()```
##cal variance

```object()```
##see the variable in rstudio  

```windows()```
##open a window with nothing inside  

```dev.off() pdf(path)```
##save the windows graph you've draw


```{r}
x = c(0,10,20)
x[0.4]#numeric(0)
```

```{r}
colors = c("brown","yellow","blue")
substr(colors , 2 ,3)
```

####use substr to pick letter from str  

```{r}
colors = c("brown","yellow","blue")
paste(colors,c(colors,"red"),sep=":")
```


   + program example  
  
###EXAMPLE1  

```{r,comment=NA}
xx = 1:20
interest_30 = 1.0025^30
intRate = 0.01
n = 10
principal = 1500
payment = principal * intRate / (1-(1+intRate)^(-n))
payment
rm("interest_30","xx") 
n <-1:10
options(width =10)
1.25*(n*0.8) - n
```

###EXAMPLE2  

```{r,comment=NA}
n <-1:10
1.25*(n*0.8) - n
 1+1/4
b = c()
for(n in 1:15){
  a = 0.8*n*1.25-n
  b = c(b,a)
}
b
```

####r calculate has some error term  
  
  
###EXAMPLE3  

```{r,comment=NA}
1+0.000000000000000001
```

####r can only calculate till 16 number after Decimal point 

###EXAMPLE4    


```{r,comment=NA}
c(1,31,1,20,20,20,5,3)%%2:3
```
####the number by order who divide by 2 and 3 and 2 and 3 ...... respectively 


   + repeat  
   
```{r,comment=NA}

rep(10,5)#REPEAT
```

```{r}
rep(c(2,3,4),each=3)
```

```{r}
rep(seq(11,30,3),c(rep(3,3),rep(4,4)))
```
####11 14 17...29 first three number will 

####repeat 3 times last 4 number will repeat

####4 times  

#CH2 factor and matrix  
    
```{r}
fac = c("A","B","A","B")
fac = factor(fac)
fac #show the levels
```
  
```{r}
fac2 = c("AAAAAAA" , "ABABABA" , "AAAAAAA" , "ABABABA",111)
fac2 = factor(fac2)
as.integer(fac2)   #trans into numbers
```
  
```{r}

fac4 = c("AAAAAAA" , "ABABABA" , "AAAAAAA" , "ABABABA")
fac4= factor(fac4)
as.integer(fac4)
levels(fac4)
levels(fac4)[as.integer(fac4)]
levels(fac4)[c(1,2,1,2,1,1,1,1,2,2,2)] #use number to create complicated factor
```

   + matrix array  

```{r}
m = matrix(20:27,nrow= 2,ncol = 4)
m
m[2,]
m[,3]#find col or row
2*m[c(1,2),c(2,4)]#linear combimation
```
  
```{r}
array(1:24, c(4,3,2))
out = array(1:120, c(5,4,3,2))
out[1,1,c(1,2),c(1,2)] #find value of specific place 
```

   + data frame  
```{r}
color = c("red","red","red1","blue")
number= c(1,3,5,7)
logic = c(T,T,F,F)
out.fr = data.frame(colors= color,numbers=number,logics=logic)
out.fr
out.fr= data.frame(color,number,logics = logic)
2*out.fr  #numeric will double 
#word will become NA

out.fr[,2] #call by name
out.fr[,"number"] #call by name

#class function shows what type of data in the variable
class(color) #character
class(logic) #logical
class(m)  #matrix
class(out.fr$color) #factor
```
  
  
#CH3  TIME
    + system time  
    
```{r}
format(Sys.time(), "%a %b %d %X %Y %Z")
format(Sys.time(), "%H %M %OS3")

lct <- Sys.getlocale("LC_TIME"); Sys.setlocale("LC_TIME", "C")
lct
x <- c("1jan1960", "2jan1960", "31mar1960", "30jul1960")
z <- strptime(x, "%d%b%Y")
x
z

dates <- c("02/27/92", "02/27/92", "01/14/92", "02/28/92", "02/01/92")
times <- c("23:03:20", "22:29:56", "01:03:30", "18:21:03", "16:56:26")
x <- paste(dates, times)
x
strptime(x, "%m/%d/%y %H:%M:%S")

z <- strptime("20/2/06 11:16:16.683", "%d/%m/%y %H:%M:%OS")
z # prints without fractional seconds
op <- options(digits.secs = 3)  #prints with fractional seconds
z
```  
  
```{r}
strptime("Tue, 23 Mar 2010 14:36:38 -0400",  "%a, %d %b %Y %H:%M:%S %z")
         
format(seq.Date(as.Date('1978-01-01'), by = 'day', len = 7), "%a")
#in day order
format(seq.Date(as.Date('2000-01-01'), by = 'month', len = 12), "%b")#in month order
seq(as.Date("2000/1/1"), as.Date("2003/1/1") ,by="week")
```

#CH4  basic graph
    + histogram  
```{r}
x= c(1:100,201:300)
hist.x=hist(x)
hist(x)
x= seq(10, 100 , 5)
y=x^3-2*x
plot(x,y) #points
plot(x,y ,type="l") #line
curve(cos,from=1,to=3*pi)
curve(x^3-2*x,from=1,to=2)
rm(x)
#curve(y^3-2*y,from=1,to=2) #function must use x to be variable
curve(tan,from=1,to=150)
```
    + saving image  
```{r}
setwd("C:/Users/Administrator/Desktop/R")
dump("hist.x","hist.x.out")
ls()
rm(hist.x)
ls()

source("hist.x.out")
ls()

dump(objects(),"all.r")
sink("try2.txt")
y = 1:10
y
x = sin(y)
x
sink()  

save.image("new.RData") 
save.image("new.www")
rm(list=ls())
load("new.RData")
ls()
```
    + function draw  

```{r}

x1 =(1:300)/100
x2 = (301:600)/100
y1=x1*3+2
y2=x2*2-(0.5*x2^2)
plot(c(0,6),c(min(y1,y2),max(y1,y2)),xlab="x",ylab="y",type="n")
curve(3*x+2,0,3,add=T)
curve(2*x-0.5*x^2,3,6,add=T)#draw by part
```
    + create random sample  
```{r}
x =rnorm(1000)
hist(x)
hist(x,breaks=5)#break into 6 parts
```
    + qq plot  
```{r}
x=rnorm(1000)
a=rnorm(1000)
qqplot(x , a , main="a and x are the same")

x=rnorm(1000)
d=exp(rnorm(1000))
qqplot(x,d, main= "D is skewed to the right")

```

```indexfinger=read.table("C:/Users/Administrator/Desktop/R/indexfinger.txt",header =T)```
####find files on computer  

```
with(indexfinger[c(3,7),],points(length, width , pch=16))
with(indexfinger[c(1,4),],points(length, width , pch=10))
plot(width~length , pch=as.character(sex),data=indexfinger)
col.v= c("red","blue", "red","red","blue","red","blue")
abline(lm( width~length,data = indexfinger ,subset=sex=="M"),lty=1 , col="blue")
abline(lm( width ~length,data = indexfinger ,subset=sex=="F"),lty=2 , col="red")
```
####some options to control the graph  
    + create from empty  
```{r}
par(mar=c(5,6,10,7)+0.1)
plot(c(1,9),c(0,50),type="n",xlab="",ylab="")
text(6,40,"Plot region")
points(6,20)
text(6,20,"(6,20)",adj=c(.5,2))#ADJ move right.5 move down 2
text(6,20,"(6,20)")
mtext(paste("Margin",1:4),side=1:4 ,line=3)#line is distance between graph and word
mtext(paste("Love",0:4),side = 1,line=0:4,at=3, cex=0.6)
#paste text beside each title ,cex control text's size(big or small)
```

#CH5 loop  
    + for  
###example
```{r}
Fibonacci = numeric(120)
Fibonacci[1] <- Fibonacci[2] <-1
for (i in 3:120) Fibonacci[i] <- Fibonacci[i-2]+ Fibonacci[i-1] 
Fibonacci
```

###example2  
```{r}
i = 0.006
for (j in 1:1000) {
  i = (1-(1+i)^(-20))/19
} 
i
```

###example3  
```{r}
Fibonacci1 = numeric(21)
Fibonacci1[1]=1
for (i in 1:20) Fibonacci1[i+1]= (Fibonacci[i+1] / Fibonacci[i]) 
Fibonacci1  #converage to 1.618034
```
###if and eilf with function
```{r}
x= 3
if (x>2) y=x^2 else y=cos(x)
y;x


corplot = function (x , y ,plotit) {
  if (plotit == TRUE) plot(x,y)
  cor (x,y)
}

corplot(c(1,3,5,7),c(2,2,10,2),F)
```
    + generate Prime number
```{r}
Eratosthenes = function(n) {
  if (n>=2) {
    sieve = seq(2,n)
    primes = c()
    for (i in seq(2,n)) {
      if (any (sieve == i)){
        primes = c(primes , i ) #PRIME is empty
        sieve = c(sieve[(sieve%%i)!=0], i)  
      }
    }
    return(primes)#send out the output
  }else{
    stop("Input value of n should be at least 2.")#stop
  }
}
n = 10 
sieve = seq(2,n)
i = 2
sieve ==i
any(sieve == i)

Eratosthenes(100)

```

```{r}
fib1 = 1
fib2 = 1
Fibonacci = c(fib1 , fib2)
while (fib2 <300){
  Fibonacci = c(Fibonacci , fib2)
  oldfib = fib2
  fib2 = fib2+fib1
  fib1 = oldfib
  print(fib2)
}
```
    + repeat  
```{r}
x = 1
tolerance = 0.000001
repeat{     #hard to fall into infinity loop
  f=x^3+2*x^2-7
  if (abs(f)< tolerance) break #can stop
  f.prime = 3*x^2+4*x
  x = x-f /f.prime
}
x
```
###same variable will not effect each 
###other under different levels
```{r}
g = function(){
  x = 2
}
f = function() {
  x = 1
  g()
  return(x)
}
f()
```
    + merge sort  
```{r}
#cut data into two parts ,combine after sorted
#front smallest compare with back smallest
#use loop RECURSION to recall function itself
mergesort = function(x){
  len= length(x)
  if(len<2) result = x 
  else{
    y = x[1:(len/2)]
    z = x[(len/2+1):len]
    y = mergesort(y)
    z = mergesort(z)
    result = c()
    while(min(length(y),length(z))>0){
      if (y[1]<z[1]){
        result = c(result, y[1])
        y  = y[-1]
      }else{
        result = c(result,z[1])
        z = z[-1]
        
      }
    }
    if(length(y)>0){
      result= c(result,y)
    }else{
      result= c(result,z)
    }
  return(result)  
  }
}
```
    
    
#CH6 more graph  
    + exp dist
```{r}
set.seed(1)
T = -log(1-runif(10000))/1
EXP = rexp(10000)
par(mfrow = c(1,2))
hist(T,breaks = 50)
hist(EXP , breaks = 50)
```
    
```{r}
set.seed(1)
k = 0.45403
g = function(x)0.5*exp(-(x^1.5))/k
x = rexp(100000)
w = g(x)/dexp(x)
curve(g(x)/dexp(x))
mean0 = weighted.mean(x ,w)#x is target w is weight
mean0
weighted.mean((x-mean0)^2,w)
```
#CH7 matrix calculate  
    + basic calculate
```{r}
cbind(seq(1,3),seq(2,4),seq(3,5))
1/cbind(seq(1,3),seq(2,4),seq(3,5))#for every element
x = matrix(c(1,2,3,1,4,9),ncol = 2)#bycol
x
dim(x)#size
x[,2]
x[,2,drop = FALSE]#matrix
class(x[,2])
class(x[,2,drop = FALSE])
rownames(x)
rownames(x) = c("obs1","obs2","obs3")#col give names
x
colnames(x)
colnames(x) = c("x","x2")
#x$x2#matrix can't use
x[,"x"]
x = as.data.frame(x)#DATAFRAME form
x$x
#det(x)  # matrix form needed
#diag(x)
y = cbind(seq(1,3),seq(2,4),seq(3,5))
y
diag(y)
diag(diag(y))#use twice become matrix
diag(1:6)
lower.tri(x)#lower triangler
x[upper.tri(x , diag=TRUE)] = 0#change upper into 0
x
x = matrix(1:6,nrow=3)
y = matrix(c(3,4,5,7,7,7),ncol=2)
x
y
x*y#element times element for each position
#x%*%y  #2*3 2*3 not allow
t(x)%*%y#TRANSPOSE
```
    + solve  
```{r}
set.seed(1)
z = matrix(rnorm(9),nrow = 3)
solve(z)
#ax=b
b = c(1,2,3)
A = z
x = solve(A,b)#find Aminus
x
```
    + AVD QR
```{r}
h3 = matrix(c(1,1/2,1/3,1/2,1/3,1/4,1/3,1/4,1/5),nrow=3)
h3
svd(h3)

qr(h3) #qr分解 AX =B QRX =B RX=T(Q)B
qr.Q(qr(h3))#Q的值
qr.R(qr(h3))#R的值

kappa(h3)#MAX eigenvalue divide MIN eigenvalue
```

```{r}
x <- cbind(x1 = 3, x2 = c(4:1, 2:5))
#col one always 3 col two 43212345
dimnames(x)[[1]] <- letters[1:8]#dim1 name
x
apply(x, 2, mean, trim = .2)
#trim  data sorted erase 20% left and right tail(trim=.2)

names(dimnames(x)) <- c("row", "col")#dim
dim(x)
x3 <- array(x, dim = c(dim(x),3),dimnames = c(dimnames(x), list(C = paste0("cop.",1:3))))
x3
#8X2X3array
apply(x,2, identity)
identical(x,  apply( x,  2,  identity))
identical(x3, apply(x3, 2:3, identity))

```

#CH8 golden function
```{r}
f = function(x){
  abs(x-3.5)+abs(x-2)+abs(x-1)
}
curve(f, from = 0 , to = 5)
golden = function(f, a , b , tol=0.0000001){
  ratio = 2/(sqrt(5)+1)
  x1 = b -ratio*(b-a)
  x2 = a+ratio*(b-a)
  f1 = f(x1)
  f2 = f(x2)
  while(abs(b-a)>tol){
    if (f2>f1){
      b=  x2
      x2 = x1
      f2 = f1
      x1 = b - ratio*(b-a)
      f1 = f(x1)
    }else{
      a = x1
      x1 = x2
      f1=f2
      x2 = a+ratio*(b-a)
      f2 = f(x2)
      
    }
  }
  return((a+b)/2)
}
golden(f,1,5)

```
#CH9 optim nlm LPsolve quadprog
```{r}
f = function(x,y)((x-y)^2+(x-2)^2+(y-3)^4)/10
x = seq(0,5,len=20)
y = seq(0,5,len=20)
z = outer(x,y,f)
contour(x,y,z)
f2 = function(x)((x[1]-x[2])^2+(x[1]-2)^2+(x[2]-3)^4)/10
optim(c(1,1),f2)#convergence = 0 is correct 

```

```
g = function(x)(abs(x-3.5)+abs(x-2)+abs(x-1))
optimize(g,c(0,5))
g1 = function(x)(abs(x-3.2)+abs(x-2)+abs(x-1)+abs(x-3.5))
optimize(g1,c(0,5))
#linear programming
install.packages("lpSolve")
library(lpSolve)
eg.lp = lp(objective.in=c(5,8),
           const.mat=matrix(c(1,1,1,2),nrow=2)
           ,const.rhs=c(2,3),const.dir=c(">=",">="))
eg.lp
eg.lp$solution

```

```
set.seed(1)
x = seq(1,5,length=20)
y = rnorm(20)+x
install.packages("quadprog")
library(quadprog)
x = cbind(rep(1,20),x) 
xx= t(x)%*%x
xy = t(x)%*%y
a = matrix(c(0,1),ncol=1)
b = 1
out = solve.QP(Dmat=xx , dvec=xy,Amat=a,bvec=b)
out
```


